A Gentle Introduction to Structural Causal Models

### 2021-05-16 scm.Rmd
draft

---
title: "A Gentle Introduction to Structural Causal Models"
author: "Daniel Saggau"
date: "5/11/2021"
output: beamer_presentation
---

@@

Regression: Omittable outside factor 
SCM/SEM; Latent influencial factor that is pivotal for the model specification but not observable

@@

>>>>

---
title: "A Gentle Introduction to Structural Causal Models"
author: "Daniel Saggau"
date: "5/11/2021"
output: beamer_presentation
citation_package: --biblatex
bibliography: [ref.bib]
---

@@

Regression: Omittable outside factor 
SCM/SEM; Latent influential factor that is pivotal for the model specification but not observable

@@

# References
